---
title: "R- For Data Science Assignment 1"
author: "VasanthKumar B"
date: "25/09/2022"
output: html_document
---

### ASSIGNMENT QUESTIONS AND SOLUTIONS

#### Introduction Exercises:  

library(tidyverse)

```{r}
```
Question  1

What happens if you make a scatterplot of class versus drv? Why is the plot not useful?
Answer:
```{r}
 ggplot(mpg, aes(x=class,y=drv))+
          geom_point()

```

Question 2

What’s gone wrong with this code? Why are the points not blue?
 ggplot(data = mpg) + 
   geom_point(aes(x = displ,y = hwy, color = "blue"))

Answer:The points are not blue because the perameter color is included with aesthetic. if color parameter is placed outside displays the points in blue color
```{r}
ggplot(data = mpg) + 
   geom_point(aes(x = displ,y = hwy), color = "blue")

```

Question 3

a) What happens if you map a aesthetic to something other than a variable name,

like aes(colour = displ<5)?

Answer:
```{r}

ggplot(data=mpg)+
    geom_point(mapping = aes(x=displ,y=hwy,color=displ<5))

```
b) What does the stroke aesthetic do? What shapes does it work with?

Answer:
```{r}
ggplot(data=mpg)+
    geom_point(aes(x=displ,y=hwy,stroke=3))

```

stroke is used to adjust the border size for shapes. it work with points(geom_point)shape.

Question 4

Read? Facet_wrap. What does nrow do? What does ncol do? What other options
control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

Answer:
The arguments nrow (ncol) determines the number of rows (columns) to use when laying out the facets. It is necessary since facet_wrap() only facets on one variable.

The nrow and ncol arguments are unnecessary for facet_grid() since the number of unique values of the variables specified in the function determines the number of rows and columns.


Question 5

a) What plots does the following code make? What does . do?

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)

```
```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)

```

b) When using facet_grid() you should usually put the variable with more unique
levels in the columns. Why?

There will be more space for columns if the plot is laid out horizontally (landscape)

Question 6

What geom would you use to draw a line chart? A boxplot? A histogram? An area
chart?


Answer:
  line_chart:geom_line()
  box_plot:geom_boxplot()
  histogram:geom_histogram()
  area_chart:geom_area()
  
Question 7

Will these two graphs look different? Why/why not?

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_point() +
geom_smooth()

```

```{r}
ggplot() +
geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```
Answer: no,the two graphs looks similar.because both geom_point() and geom_smooth()
use same data and mappings

Question 8

What does geom_col() do? How is different to geom_bar()?

Answer:
  The geom_col() function has different default stat than geom_bar(). The default stat of geom_col() is stat_identity(), which leaves the data as is. The geom_col() function expects that the data contains x values and y values which represent the bar height.

The default stat of geom_bar() is stat_count(). The geom_bar() function only expects an x variable. The stat, stat_count(), preprocesses input data by counting the number of observations for each value of x. The y aesthetic uses the values of these counts.


  Question 9
  
  What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
  
Answer:
```{r} 
  ggplot(data=diamonds)+
  geom_pointrange(mapping=aes(x=cut,y=depth),
                  stat ="summary",
                  fun.ymin =min,
                  fun.ymax =max,
                  fun.y =median)

 
```  


Question 10

What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?

Answer:
```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()

```



